% #############################################################################
% Agradecimentos / Acknowledgments
% !TEX root = ../main.tex
% #############################################################################

First and foremost, I want to thank my mother, father and sister for always supporting me throughout all these years. Thank you for always encouraging and comforting me in the most difficult times.

A special thank you to Professor Margarida Silveira for trusting me to carry out this work and for all the motivation and guidance she has given me during this work. 

A deep thank you to Hemaxi Narotamo for all the availability, support and for always giving me the most helpful and necessary suggestions.

I would also like to thank my hometown and oldest friends who witnessed all my progress and stood by me even when I wasn't around much. They were there to celebrate the good moments and motivate me in the bad ones. Thank you, Bárbara Jesus, Inês Monteiro, Margarida Santos and Maria Araújo.

I also want to thank all the people from NEECIST and JEECIST for making a safe space for me to grow and develop. A special thank you to Maria Inês Conceição, Vasco Rodrigues, Eduardo Cunha, Pedro Pedrosa and Ricardo Espadinha for putting up with me and all my existential crises and always pushing me to improve.

And of course a special thank you to my friends and colleagues who have been with me since the first year and without whom I would not have come this far. They have made all the late nights working on projects and studying for exams worthwhile. Thank you for all the support and laughter Beatriz Pereira, Aprígio Malveiro, Francisco Galante and Catarina Almeida.

Last but not least, I would like to thank ISR, SIPG and DSOR for welcoming me and giving me the space to do this work and making me laugh. Special thanks to Eduardo and David Souto.